Decentralised Authoring, Annotations and Notifications for a Read-Write Web with dokieli

### 2017-04-05 index.tex
Add figures

  \item[Web of Trust] The Web as a collaborative medium makes it possible for people to take responsibility (or be accountable) for their contributions. It should be possible for people to publish, share, and annotate information while ensuring their provenance, authenticity and integrity ~\cite{ref-5, ref-6, ref-7}.
\end{description}

@@

\par Figure 1 depicts the contrast between typical centralised and decentralised architectures.

                                        Typical centralised and decentralised architectures

@@

\par On the other hand, if desired and available, users can participate using their own profiles (WebIDs) located anywhere on the Web, and get to store and make their annotations in their own personal storage, as well as assign access controls to documents. Similarly, a decentralised communications protocol, \empty Linked Data Notifications~\cite{ref-9} (W3C Proposed Recommendation~\cite{ref-10}), is used get past the limits of centralisation by enabling communication to happen across independent servers. Figure 2 depicts relations between the kinds of entities which underlay dokieli’s architecture, where nodes are under different domains and authority.

                                        Entities and relations within dokieli’s architecture

@@

                                        \empty Video of dokieli Web Annotation

                                        \empty Video of dokieli Share

@@

                                        \empty Video of semantic inline citations

                                        \empty Video of Sparqlines interaction in dokieli

>>>>

  \item[Web of Trust] The Web as a collaborative medium makes it possible for people to take responsibility (or be accountable) for their contributions. It should be possible for people to publish, share, and annotate information while ensuring their provenance, authenticity and integrity ~\cite{ref-5,ref-6,ref-7}.
\end{description}

@@

\par Figure ~\ref{fig:centralised-decentralised-architectures} depicts the contrast between typical centralised and decentralised architectures.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{media/images/centralised-decentralised-architectures}
  \caption{Entities and relations within dokieli’s architecture}
  \label{fig:centralised-decentralised-architectures}
\end{figure}

@@

\par On the other hand, if desired and available, users can participate using their own profiles (WebIDs) located anywhere on the Web, and get to store and make their annotations in their own personal storage, as well as assign access controls to documents. Similarly, a decentralised communications protocol, \empty Linked Data Notifications~\cite{ref-9} (W3C Proposed Recommendation~\cite{ref-10}), is used get past the limits of centralisation by enabling communication to happen across independent servers. Figure ~\ref{fig:dokieli-architecture-relations} depicts relations between the kinds of entities which underlay dokieli’s architecture, where nodes are under different domains and authority.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{media/images/dokieli-architecture-relations}
  \caption{Typical centralised and decentralised architectures}
  \label{fig:dokieli-architecture-relations}
\end{figure}

@@

\begin{figure}
  \begin{minipage}[b]{.49\textwidth}
    \includegraphics[width=\textwidth]{media/images/dokieli-annotation}
    \caption{dokieli Web Annotation}
    \label{fig:dokieli-annotation}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{.49\textwidth}
    \includegraphics[width=\textwidth]{media/images/dokieli-share}
    \caption{dokieli Share}
    \label{fig:dokieli-share}
  \end{minipage}
\end{figure}

@@

\begin{figure}
  \begin{minipage}[b]{.49\textwidth}
    \includegraphics[width=\textwidth]{media/images/dokieli-citation}
    \caption{Semantic inline citations in dokieli}
    \label{fig:dokieli-citation}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{.49\textwidth}
    \includegraphics[width=\textwidth]{media/images/dokieli-sparqlines}
    \caption{Sparqlines interaction in dokieli}
    \label{fig:dokieli-sparqlines}
  \end{minipage}
\end{figure}
